Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-01 aosd13/pepm13/caseStudyImpl.tex
Fix overfull hboxes

%We use enrich-my-library again with an implicit conversion to \code{TraversableLikeOps[T, Repr]}, shown later, which corresponds to
%\code{TraversableLike[T, Repr]}.
%We provide an implicit conversion to \code{TraversableLikeOps[T, Repr]} from \code{Exp[Repr]} for any type \code{Repr} which is a subtype of \code{TraversableLike[T, Repr]} and \code{Traversable[T]} (for some element type \code{T}). This can be expressed as:
\begin{lstlisting}
implicit def expToTraversableLikeOps[T,
  Repr <: Traversable[T] with TraversableLike[T, Repr]](v: Exp[Repr]) =
    new TraversableLikeOps[T, Repr](v)
\end{lstlisting}

>>>>

%We use enrich-my-library again with an implicit conversion to \code{TraversableLikeOps[T, Repr]}, shown later, which corresponds to
%\code{TraversableLike[T, Repr]}.
%We provide an implicit conversion to \code{TraversableLikeOps[T, Repr]} from \code{Exp[Repr]} for any type \code{Repr} which is a subtype of \code{TraversableLike[T, Repr]} and \code{Traversable[T]} (for some element type \code{T}). This can be expressed as:
\begin{lstlisting}
implicit def expToTraversableLikeOps
  [T, Repr <: Traversable[T] with TraversableLike[T, Repr]](v: Exp[Repr]) =
    new TraversableLikeOps[T, Repr](v)
\end{lstlisting}
